%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Jingmin}{Yu}
\address{3700 SW 27th St D-306, Gainesville, FL, 32608}
\mobile{(+1) 352-222-1481} 
%%% Social
\email{jmyu1994@ufl.edu}
%\homepage{www.posquit0.com}
\github{jmyu1994}
\linkedin{jingmin-yu}
%%% Optionals
%\position{Software Engineer{\enskip\cdotp\enskip}Security Expert}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {company name}
\letterdate{\today}
\lettertitle{Job Application for Software Engineer}
\letteropening{Dear Hiring Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Jingmin Yu~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
I am a graduate student at University of Florida(UF). I will be graduating with a Master of Science degree in Computer Science in May 2018. I am looking for a full-time job or as a software development engineer in your company. I firmly believe that my education and previous programming experience qualify me for this position.
	
\cvparagraph{Why Me}
While pursuing my Master's degree in Computer Science, I learned many useful software development skills and had thorough understanding of data structures and algorithms. I developed some java and android applications. I also designed several simple web pages and completed some big-data-related work. I’ve attached a copy of my resume that details my projects and experience. I enjoy being challenged and working on projects that require me to work outside my comfort and knowledge set, as continuing to learn new languages and development techniques are of great importance to me and the success of your organization. 

\cvparagraph{Contact Me}
As an engineer eager to learn new techniques and make a contribution to an outstanding company, I am excited to submit my application for consideration. If you would like to discuss my qualifications further, please feel free to contact me at (352) 222-1481 or at jmyu1994@ufl.edu. Thank you so much for your time and consideration. I look forward to hearing from you.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
